Make any stupid plot you want

### 2021-02-10 draft/sections/intro.tex
criteria

\subsection{What even is a data visualization library?}
 Byrne et al. describe visualizations as having graphic and figurative components; graphic representations are maps from data values to visual encodings, while figurative representations have meaning due to their similarity in shape to external concepts \cite{byrneAcquiredCodesMeaning2016}. For example, the Du Bois data portraits in figure~\ref{fig:intro_dubois} are mostly graphic representations where quantitative variables are mapped to glyph segment length or area. Du Bois combines a graphical representation where glyph size varies by population with a figurative representation of those glyphs as the countries the data is from in figure~\ref{fig:intro_dbc}. So given graphics by definition have an underlying data

 Data visualizations originated as maps of places and stars \cite{friendlyBriefHistoryData2008}; direct graphical representations of physical items in space. While often decorative, to be useful these visualizations at least somewhat had to preserve some notion of relative distance between the objects being graphed, which Tufte termed the Lie principal\cite{tufteVisualDisplayQuantitative2001}.

Mackinlay defines two criteria for

>>>>

\subsection{What even is a data visualization library?}
This work aims to develop a model of visualization such that a tool built using this model could support visualizations as varied as those of Du Bois in figure~\ref{fig:}; to do so, we first discuss the criteria by which a visualization is evaluated.

Byrne et al. describe visualizations as having graphic and figurative components; graphic representations are maps from data values to visual encodings\cite{bertinSemiologyGraphicsDiagrams2011a}, while figurative representations have meaning due to their similarity in shape to external concepts \cite{byrneAcquiredCodesMeaning2016}. In figure~\ref{fig:intro_dbc}, Du Bois combines a graphical representation where glyph size varies by population with a figurative representation of those glyphs as the countries the data is from, which means that the semantic nominal and numerical properties of the data are preserved in the graph. Norman states that when the properties of the representation match the properties of the information being represented\cite{norman_things_smart, NaturalnessPrincipleInfoVis} then the visualizations are more understandable 
, but does not give criteria for what it means for the properties to match. Tufte specifies that visual representations must be in proportion to the quantitative data being represented, but otherwise his notion of graphic integrity is heavily context dependent\cite{tufteVisualDisplayQuantitative2001}.

Mackinlay
